Silenced in the Chamber: Analyzing Gendered Speech Interruptions in the Australian Parliament (1998–2022)

### 2025-01-15 paper/paper.qmd
update paper name

---
title: "Gender Dynamics of Parliamentary Interruptions: A Detailed Analysis of Speech Disruptions in the Australian Parliament (1998-2022)"
subtitle: "My subtitle if needed"
author: 
  - Hannah Yu
  - Rohan Alexander
thanks: "Code and data are available at: https://github.com/hannahyu07/Hansard_Interruptions"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Silenced in the Chamber: Analyzing Gendered Speech Interruptions in the Australian Parliament (1998–2022)"
subtitle: "My subtitle if needed"
author: 
  - Hannah Yu
  - Rohan Alexander
thanks: "Code and data are available at: https://github.com/hannahyu07/Hansard_Interruptions"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
